Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-08 thesis/thesis.tex
thesis: Review Aims

The main aim of this thesis is to \emph{build an unsupervised clustering model for open cluster characterization}.
The model will be \emph{non-supervised and non-parameterized} to fit a wide range of clusters without
the need for fine-tuning a high number of hyperparameters.

@@

\begin{itemize}
  \item Gather information on the \emph{state of the art}.
  \item Research unsupervised clustering algorithms suitable for grouping stars previously recovered.
  \item Recover data from Gaia DR2 database. This data will be taken as source for the machine learning model to characterize open clusters
  by grouping stars into clusters.
  \item Select and implement unsupervised clustering algorithms from the previous study.
  \item Use those algorithms with different datasets to find OCs.
  \item Look for an independent method to characterize OCs in order to make comparisons.
  \item Validate found OCs with our custom model by making comparisons with the independent method.
\end{itemize}

>>>>

The primary aim of this thesis is to \emph{build an unsupervised clustering model for open cluster characterization}.
The model will be \emph{non-supervised and non-parameterized} to fit a wide range of clusters without
the need for fine-tuning a high number of hyperparameters.

@@

\begin{itemize}
  \item Gather information on the \emph{state of the art}.
  \item Research unsupervised clustering algorithms suitable for grouping stars previously recovered.
  \item Recover data from Gaia DR2 database. This data will be taken as source for the machine learning model to characterize open clusters
  by grouping stars into clusters.
  \item Select and implement unsupervised clustering algorithms from the previous study.
  \item Use chosen algorithms with different datasets to find OCs.
  \item Look for an independent technique to use it as a validation method.
  \item Validate OCs found with our custom model by making comparisons with the validation method.
\end{itemize}
